Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-22 journal/article.tex
S: Communities, alignment

@@

>>>>

% * Create a sense of urgency
% * Find a common cause to motivate the change
% [P11]
% Find a rallying point.  You might not have a recession as a spur to receptivity,
% but a common, critical cause to motivate change will make it easier to explain
% how Scrum can contribute to the success  of that cause.

@@

The formation and influence of agile communities was reported to have a
significant impact on transformation.
The emergence of an agile community was reported as a success factor in the
transformation [P3]. A community was also seen as indispansable as it has power
to overcome impediments that would be too large for individuals to affect [P47].
The agile communities achieved to raisie awareness of agile methods in the
organization [P42, P41, P47], and spawned eager followers who spread the word
even further [P12].

A factor in achieving change was creating alignment towards the common goal of
introducing a new development method. It was seen as an important factor that
all levels in the organization speak the same language and accept the change
[P18, P31]. Alignment was built by promoting success stories and gathering lists
of problems to tackle [P42, P46]. In one case complete alignment between teams
and within management was considered as necessary to use the agile model in a
large context [P43]. Another case highlighted creating and applying a structured
rollout process to uniformly introduce a large nuber of teams to agile [P8].

\subsubsection{Management support}

The most prominent and clear success factor was having support from management.
